 

### 2020-09-02 vertical-thermal-review.Rmd

---
title: ''
output: word_document
bibliography: references.bib #This can be generated by exporting BibTex file from Zotero
csl: new-phytologist.csl 
nocite: | 
  @zellweger_seasonal_2019 
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

**Table 1. Summary of observed variation in thermally-relevant leaf traits with canopy height and/or between sun and shade leaves** ([*GitHub issue #9*](https://github.com/EcoClimLab/vertical-thermal-review/issues/9))

@@

**Table 2. Summary of observed variation in leaf metabolism and thermal responses across the vertical gradient and/or between sun and shade leaves** ([*GitHub issue #9*](https://github.com/EcoClimLab/vertical-thermal-review/issues/9))

@@

**VOC production**

@@

@@

![**Figure 4. Temperature sensitivity of tree growth for understory versus canopy trees.** Analysis methods described in Appendix S3. Data from Helcoski et al. 2019.](SCBI_tree_rings/SCBIfig.png)
## Implications for Modeling / Scaling

>>>>

---
title: ''
output: word_document
bibliography: references.bib #This can be generated by exporting BibTex file from Zotero
csl: new-phytologist.csl 
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

![(*For latest version of table, see tables.pdf.*)](table1.png)
```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @zellweger_seasonal_2019 
---

@@

![(*For latest version of table, see tables.pdf.*)](table2.png)
```{r eval=FALSE, echo=FALSE}
# refs in this table need to go in the nocite field below
```
---
nocite: | 
  @zellweger_seasonal_2019 
---

*Stomatal conductance*

*Photosynthesis*

@@

@@

*Respiration*

*VOC production*

@@

![**Figure 4. Temperature sensitivity of tree growth for understory versus canopy trees.** Analysis methods described in Appendix S3. Data from Helcoski et al. 2019.](SCBI_tree_rings/SCBIfig.png)

## Implications for Modeling / Scaling
